% ====================
% EXPERIENCE A
% ====================
\subsection{{Senior Frontend developer - Jan 2023 – Present}}
\subtext{\href{https://snapp.com}{SNAPP} \textcolor{gray}{- {\small Fulltime}}}
\vspace{0.8em}{\color{black}{\small\textit{A ride-sharing and transportation service (similar to Uber or Lyft) serving over 40 million users across the Middle East}}}\par\vspace{-.75em}
\begin{zitemize}
\setlength{\itemsep}{0.2em}
\item \textbf{Developed} and \textbf{maintained} the frontend of the snapp application, a ride-sharing platform
\item \textbf{Proposed} and \textbf{implemented} a feature allowing users to search their location in-app by latitude and longitude, used \textbf{5K} times on the first day of release.
\item Developed a chat feature for the application, with \textbf{EMQ} and Socket.io, used \textbf{100K} times on the first day of release.
\item \textbf{Enhanced} codebase maintainability by restructuring from a \textbf{flat folder structure} into a \textbf{feature-based architecture}.
\item \textbf{Enhanced} the application performance by replacing \textbf{CSS-in-JS (styled-components)} UI Kit module with \textbf{Panda CSS}, making the module \textbf{tree-shakable} and reducing \textbf{bundle size}.
\item \textbf{Managed} application deployments using \textbf{OpenShift} and \textbf{Argo CD}.
\end{zitemize}

\vspace{0.5em}
\subsection{{Chapter Leader Frontend - Mar 2021 – Jan 2023}}
\subtext{\href{https://arvancloud.ir}{ArvanCloud} \textcolor{gray}{- {\small Fulltime}}}
\vspace{0.8em}{\color{black}{\small\textit{Cloud services and infrastructure platform like Cloudflare and AWS in Iran with 1k+ customers}}}\par\vspace{-.75em}
\begin{zitemize}
\setlength{\itemsep}{0.2em}
\item \textbf{Managed} team delivery and \textbf{improvement}, including \textbf{responsibility delegation} and enhancing
    team communication.
\item \textbf{Developed} Micro Front-end infrastructure for panel.arvancloud.ir with \textbf{Webpack Module Federation},
enabling independent staging and production releases for micro-apps.
\item Oversaw team routines such as \textbf{one-on-one meetings}, \textbf{iteration planning}, and \textbf{retrospectives}.
\item Made \textbf{strategic} technical \textbf{decisions} to support \textbf{team} objectives.
\item \textbf{Managed} team \textbf{delivery} and \textbf{improvement}, including responsibility \textbf{delegation} 
\end{zitemize}

\vspace{0.5em}
\subsection{{Senior Frontend developer - Aug 2019 – Mar 2021}}
\subtext{\href{https://arvancloud.ir}{ArvanCloud} \textcolor{gray}{- {\small Fulltime}}}
\begin{zitemize}
\setlength{\itemsep}{0.2em}
\item \textbf{Led} the recruitment and hiring of \textbf{6} top-performing senior to mid-level front-end engineers.
\item \textbf{Optimized} the project by \textbf{removing unnecessary npm packages}, \textbf{creating shared components} to eliminate code duplication, and \textbf{refactoring legacy code} for better project structure, resulting in a significant reduction of the main bundle file size from \textbf{4MB} to approximately \textbf{1MB}.
\item \textbf{Experienced} with \textbf{Sentry} for issue management.
\end{zitemize}

\vspace{0.5em}
\subsection{{Frontend developer - Feb 2016 – Aug 2019}}
\subtext{\href{https://kamva.ir}{Kamva} \textcolor{gray}{- {\small Fulltime}}}
\vspace{0.8em}\textcolor{black}{\small\textit{E-commerce platform and shop builder like Shopify in Iran}}\par\vspace{-.75em}
\begin{zitemize}
\setlength{\itemsep}{0.2em}
\item Developed an \textbf{SSR} project that dynamically renders e-commerce shops and integrates with Iran’s bank web gateways. with \textbf{React}, \textbf{Redux}, \textbf{Redux-saga}, \textbf{NodeJS}.
\item Created an easy-to-use \textbf{theme editor} with drag-and-drop \textbf{functionality}, allowing \textbf{users} to customize their shop themes.
\item Experienced with \textbf{Express.js} and \textbf{MongoDB} to build an \textbf{internal} day‑off \textbf{full-stack} booking app.
\item \textbf{Experienced} with technologies and concepts including Webpack, SSR, Redux.
\end{zitemize}




